### 2020-05-12 Report/aws_325ghz_study.tex
Some rearrangement of the comparison with ATMS.

[* Do we show comparison to ATMS, or do we refer to articles for ``validation''? ]
[* Add time and latitude ranges used * ]

@@

For water vapour the present settings in RTTOV are applied. That is, largely
MPM89 \citep{liebe:89} is followed, but some parameters for the 22 and 183\,GHz
transitions are replaced \citep{saunders2018update,turner2019amsutran}. A basic
comparison to RTTOV (12.?) was made (with MHS as assumed sensor) and an
agreement around or better than 0.?\,K was found [* expand *].

@@

@@

>>>>

@@

For water vapour the present settings in RTTOV are applied. That is, largely
MPM89 \citep{liebe:89} is followed, but some parameters for the 22 and 183\,GHz
transitions are replaced \citep{saunders2018update,turner2019amsutran}.

@@

\subsection{Validation of simulations}
%
Using the simulation setup described above, around 77000 cases were simulated
based on randomly selected CloudSat orbits during August 2015. The input data
were restricted between $60^{\degree}$S to $60^{\degree}$N. No differentiation
was made between the observations over water and land.

\begin{figure}[p]
	\centering
	\includegraphics[height=60mm]{ATMS_C16_distribution}\hspace{5mm}% 
	\includegraphics[height=60mm]{ATMS_C17_distribution}
	\includegraphics[height=60mm]{ATMS_C18_distribution}\hspace{5mm}% 
	\includegraphics[height=60mm]{ATMS_C19_distribution}
	\includegraphics[height=60mm]{ATMS_C20_distribution}\hspace{5mm}% 
	\includegraphics[height=60mm]{ATMS_C21_distribution}
	\includegraphics[height=60mm]{ATMS_C22_distribution}
	\caption{Probability distribution functions (PDFs) of simulated and
      observed ATMS channels brightness temperatures for channels 16 - 22 and
      nadir viewing angle. The data covers latitude range $60^{\degree}$S to
      $60^{\degree}$N. Both land and ocean measurements are considered and only
      daytime ATMS data are included. See further the text.}
	\label{fig:pdf:c16-22}
\end{figure}

A statistical comparison of the simulations to actual ATMS data, for channels
16-22 at nadir (zenith angle = $180^{\degree}$), is shown in
Figure~\ref{fig:pdf:c16-22}. For the comparison, the daytime ATMS observations
were selected as CloudSat operates only during the day part of the orbit since
2011. For the channels around 183\,GHz, the ATMS characteristics are not fully
simulated. The ATMS channel widths are considered, but as AWS is only covering
the lower wing of the 183\,GHz transition the upper sideband of ATMS is not
included.

The overall agreement is good for channels. For 183 GHz channels (Channels
18-22), the simulations and observations have a good agreement for the part of
the PDFs matching clear-sky conditions (the main peak of the distribution),
albeit the simulations have a more sharp peak. This could either be caused by a
different geographical sampling of ATMS and CloudSat or to shortcomings in the
ERA-Interim input data. The fraction of cloudy observations is lower in ATMS in
comparison to simulations, for brightness temperatures below about 240\.K. This
is due to the fact that the antenna pattern is not considered in the
simulations.

In the intermediate region, the simulations have a lower occurance rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citep{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher overrepresentation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresentated in the results.

@@

\section{Cloud correction by a simple scheme}
%
\dots

\section{Cloud correction by QRNN}
%
\dots
